---
title: "ASSIGMENT 1 - REPRODUCIBLE RESEARCH"
author: "Daiane Rodrigues"
date: "9 de dezembro de 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```




&nbsp;

#####1)IMPORT DATA SET 

```{r p1}
library(readr)
activity = as.data.frame(read_csv("C:/Users/Daiane/Desktop/COURSERA/REPRODUCIBLE RESEARCH/SEMANA2/activity.csv"
,col_types = cols(date = col_date(format = "%Y-%m-%d"))))

```
&nbsp;


#####Show data set 

```{r p2}
head(activity)
```


&nbsp;


#####Make a new data set whith a new variable that sum all steps, for each day

```{r p3 ,message=FALSE}
library(dplyr)
  st <- activity %>%
    filter(!is.na(steps)) %>%
    group_by(date) %>%
    summarize(st_soma = sum(steps)) %>%
    print
```

&nbsp;

#####2)Histogram of the total number of steps taken each day 

```{r g1, message=FALSE}
library(ggplot2)
qplot(st$st_soma,geom = 'histogram',main = "Histogram for Steps", ylab = "steps")
```
&nbsp;


#####3)Mean and median number of steps taken each day

```{r p4 ,message=FALSE}
mean(st$st_soma)
median(st$st_soma)
```
&nbsp;


#####4)Time series plot of the average number of steps taken

*  Calculation of the mean, for each day
```{r p5 ,message=FALSE}
st2 <- activity %>%
    filter(!is.na(steps)) %>%
    group_by(date) %>%
    summarize(st_media = mean(steps)) %>%
    print
```

*  Plot of the mean

```{r g2, message=FALSE}
qplot(x=st2$date,
      y=st2$st_media,
      geom = c("line"),main = "Mean of steps for date", ylab = "steps")
```

&nbsp;


#####5)The 5-minute interval that, on average, contains the maximum number of steps


*  Calculation of the mean, for each interval
```{r p6 ,message=FALSE}
interval = activity %>%
    filter(!is.na(steps)) %>%
    group_by(date) %>%
    summarize(st_media = mean(steps)) %>%
    print
```

*  found the interval with the longer interval
```{r p7 ,message=FALSE}
interval[which.max(interval$st_media),]
```

&nbsp;


#####6)Code to describe and show a strategy for imputing missing data
*  Replacee the missing values

```{r p8 ,message=FALSE}
data_subs = activity
na = is.na(data_subs$steps)

avg = tapply(data_subs$steps, data_subs$interval, mean, na.rm=TRUE, simplify=TRUE)
data_subs$steps[na] = avg[as.character(data_subs$interval[na])]
```

*  Calculating the steps

```{r p9 ,message=FALSE}
steps_subs <- data_subs %>%
  filter(!is.na(steps)) %>%
  group_by(date) %>%
  summarize(steps = sum(steps)) %>%
  print
```

&nbsp;

#####7)Histogram of the total number of steps taken each day after missing values are imputed 

```{r g3, message=FALSE}
qplot(steps_subs$steps,geom = 'histogram',main = "Histogram for Steps", ylab = "steps after replace missing values")
```

&nbsp;

*  Calculation of the mean and the median, including missing values

```{r p10 ,message=FALSE}
mean(steps_subs$steps)
median(steps_subs$steps)
```

&nbsp;

#####8)Panel plot comparing the average number of steps taken per 5-minute interval across weekdays and weekends

&nbsp;

*  Difference between weekday weekend

```{r p11 ,message=FALSE}
data_subs2 = mutate(data_subs, weektype = ifelse(weekdays(data_subs$date) == "sábado" | weekdays(data_subs$date) == "domingo", "weekend", "weekday"))

data_subs2$weektype = as.factor(data_subs2$weektype)
head(data_subs2)
```
&nbsp;
  
  *  Average steps in five minutes intervals
  
```{r p12 ,message=FALSE}
  interval_subs =  data_subs2 %>%
    group_by(interval, weektype) %>%
    summarise(steps = mean(steps))
```
  
  &nbsp;
  
  *  Plot of the Graph
  
```{r g4, message=FALSE}
p = ggplot(interval_subs, aes(x=interval, y=steps, color = weektype)) +
  geom_line() +
  facet_wrap(~weektype, ncol = 1, nrow=2)
print(p)
```



































